Compilation and Backend-Independent Vectorization for Multi-Party Computation

### 2022-05-01 overleaf/introduction.tex
Minor edits in these secs.

Earlier compilers did both back-end and front-end translation without a specific focus on either, as their aim was to demonstrate applicability of MPC on real-world
programming problems. As the field advanced, works have focused more closely on front-end language design (e.g., Wysteria~\cite{SP:RasHamHic14} and Viaduct~\cite{Acay:2021})
or back-end ``circuit-level'' design and implementation (e.g., MOTION~\cite{Braun:2022}).

@@

We use the MPC Source~\cite{Ishaq:2019} intermediate representation and emphasize optimization over MPC Source. As in classical compilers, we envision different front ends (e.g., our front end IMP Source, other) compiling into MPC Source. MPC Source is particularly suitable for optimizations such as protocol mixing~\cite{Ishaq:2019, Fang:2022} and SIMD-vectorization,
which takes advantage of amortization at the circuit level. The MPC Source IR exposes the linear structure of MPC programs, which simplifies program analysis; this is
in contrast to source, which has if-then-else constructs. In the same time, MPC Source is sufficiently ``high-level''  to support analyses and optimizations that take into account
control and data flow in a specific program. MPC Source is small in size and analysis is tractable, as opposed to analysis over an unrolled circuit~\cite{Ishaq:2019}. Again as
in classical compilers, we envision translation of MPC Source (optimized or unoptimized) into MOTION, SPDZ, or other back-end code.

>>>>

Earlier compilers did both back-end and front-end translation as their aim was to demonstrate applicability of MPC on real-world
programming problems. As the field advanced, works have focused more closely on front-end language design (e.g., Wysteria~\cite{SP:RasHamHic14} and Viaduct~\cite{Acay:2021})
or back-end ``circuit-level'' design and implementation (e.g., MOTION~\cite{Braun:2022}).

@@

We formalize the MPC Source~\cite{Ishaq:2019} intermediate representation and emphasize optimization over MPC Source. As in classical compilers, we envision different front ends (e.g., our front end IMP Source, other) compiling into MPC Source. MPC Source is particularly suitable for optimizations such as protocol mixing~\cite{Ishaq:2019, Fang:2022} and SIMD-vectorization,
which takes advantage of amortization at the circuit level. The MPC Source IR exposes the \emph{linear structure} of MPC programs, which simplifies program analysis; this is
in contrast to source, which has if-then-else constructs. In the same time, MPC Source is sufficiently ``high-level''  to support analysis and optimizations that take into account
control and data flow in a specific program. MPC Source facilitates cost modeling. 
%MPC Source is small in size and analysis is tractable, as opposed to analysis over an unrolled circuit~\cite{Ishaq:2019}. 
Again as in classical compilers, we envision translation of MPC Source (optimized or unoptimized) into MOTION, SPDZ, or other back-end code.

### 2022-05-01 overleaf/results.tex
Minor edits in these secs.

\subsection{Experiment Setup}\label{sec:experiment_setup}
We tested our framework with several benchmarks. For the multiparty computation (MPC), we restriced our evaluation to 2 party computation (2PC) setting because it requires fewer computing resources. We stress that there is no such inherent restriction in our framework. We use hardware resources provided by CloudLab\cite{DuplyakinATC19} and consider two network settings, namely Local Area Netowrk (LAN) and Wide Area Network (WAN). In the LAN setting, we use {\tt c6525-25g} machines for both parties. These machines are equipped with 16-core AMD 7302P 3.0GHz processors and 128GB of RAM. The connection between these machines had 10Gbps bandwidth and sub-millisecond latency. This setting reflects typical LAN usecase considering that 10Gbps LAN is increasingly common in business networks and is now available even in some home networks. For WAN setting, we again used a {\tt c6525-25g} machine (located in Utah, US) for the first party and a {\tt c220g1} machine (located in Wisconsin, US) for the second. The {\tt c220g1} machine is equiped with two Intel E5-2630 8-core 2.40GHz processors and 128GB of RAM. We measured the connection bandwidth between these machines to be 560Mbps and average round trip time (RTT) to be 38ms. At the time of this writing, all major internet providers in the US offer 1Gbps connections to home consumers, therefore this setting reasonably reflects the typical WAN usecase.

We run all experiments 5 times and report average values of various metrics. Note that standard deviation--shown as errorbar on top of the bars in the graphs--in all observations was at most 4.5\% of the mean value, therefore the accuracy of the results is not effected by the relatively fewer runs.

>>>>

\subsection{Experiment Setup}\label{sec:experiment_setup}
We tested our framework with several benchmarks. For the multiparty computation (MPC), we restriced our evaluation to 2 party computation (2PC) setting because it requires fewer computing resources. We stress that there is no such inherent restriction in our framework. We use hardware resources provided by CloudLab\cite{DuplyakinATC19} and consider two network settings, namely Local Area Netowrk (LAN) and Wide Area Network (WAN). In the LAN setting, we use {\tt c6525-25g} machines for both parties. These machines are equipped with 16-core AMD 7302P 3.0GHz processors and 128GB of RAM. The connection between these machines had 10Gbps bandwidth and sub-millisecond latency. This setting reflects typical LAN usecase considering that 10Gbps LAN is increasingly common in business networks and is now available even in some home networks. In the WAN setting we again used a {\tt c6525-25g} machine (located in Utah, US) for the first party and a {\tt c220g1} machine (located in Wisconsin, US) for the second. The {\tt c220g1} machine is equiped with two Intel E5-2630 8-core 2.40GHz processors and 128GB of RAM. We measured the connection bandwidth between these machines to be 560Mbps and average round trip time (RTT) to be 38ms. At the time of this writing, all major internet providers in the US offer 1Gbps connections to home consumers, therefore this setting reasonably reflects the typical WAN usecase.

We run all experiments 5 times and report average values of various metrics. Note that standard deviation --- shown as errorbar on top of the bars in the graphs --- in all observations was at most 4.5\% of the mean value, therefore the accuracy of the results is not effected by the relatively fewer runs.
